Fractional Types

### 2019-11-23 fracGC/p.tex
fix typo
A pass from sec 1-4

\newunicodechar{⊸}{$\multimap$}
\newunicodechar{Π}{$\Pi$}
\newunicodechar{≟}{$\mathbin{\stackrel{?}{=}}$}
\newunicodechar{𝕌}{$\mathbb{U}$}
\newunicodechar{𝔹}{$\mathbb{B}$}
\newunicodechar{𝔽}{$\mathbb{F}$}
\newunicodechar{𝕋}{$\mathbb{T}$}
\newunicodechar{𝟘}{$\mathbb{0}$}
\newunicodechar{𝟙}{$\mathbb{1}$}
\newunicodechar{𝟚}{$\mathbb{2}$}
\newunicodechar{⋆}{${}_*$}
\newunicodechar{○}{$\gcv$}
\newunicodechar{ᵤ}{${}_u$}
\newunicodechar{⊚}{$\fatsemi$}
\newunicodechar{⟷}{$\leftrightarrow$}
\newunicodechar{⟶}{$\longrightarrow$}
\newunicodechar{⟪}{$\ll$}
\newunicodechar{⟫}{$\gg$}
\newunicodechar{⊎}{$\uplus$}
\newunicodechar{ₗ}{$_l$}
\newunicodechar{ᵣ}{$_r$}
\newunicodechar{❰}{$\llparenthesis$}
\newunicodechar{❱}{$\rrparenthesis$}

@@

Below, we show code that defines types corresponding to bits (booleans),
two-bits, three-bits, and four-bits. We then define an operator that
builds a controlled version of a given combinator $c$. This controlled
version takes an additional ``control'' bit and only applies $c$ if
the control bit is true. The code then iterates the control operation
several times starting starting from boolean negation.

@@

By construction, the \AgdaFunction{TOFFOLI} function takes three bits,
and negates the third if the first two are both true. As
Toffoli~\cite{Toffoli:1980} demonstrated, this function is universal
for classical reversible circuits assuming it is possible to allocate
and de-allocate ancilla bits. Indeed without using ancilla bits, it is
not possible to use compositions of \AgdaFunction{TOFFOLI} functions
to implement more general versions that are controlled by more than
two bits (for example, \AgdaFunction{CTOFFOLI}). The proof is simple:
the \AgdaFunction{TOFFOLI} function depends on two control bits and
possibly negates a third; when used in a circuit with four bits, the
unused bit can be either state, which means that
\AgdaFunction{TOFFOLI} generates an even permutation. The function
\AgdaFunction{CTOFFOLI} is however an odd permutation which is
unreachable from even permutations. This function will however be
definable once we introduce ancilla bits in the next section.

@@

\begin{figure}[ht]
  \PIFDtoffoli{}
\caption{\label{fig:toff}Generalized Toffoli Gates}
\end{figure}

>>>>

\newunicodechar{⊸}{$\multimap$}
\newunicodechar{Π}{$\Pi$}
\newunicodechar{≟}{$\mathbin{\stackrel{?}{=}}$}
\newunicodechar{𝕌}{$\mathbb{U}$}
\newunicodechar{𝔹}{$\mathbb{B}$}
\newunicodechar{𝔽}{$\mathbb{F}$}
\newunicodechar{𝕋}{$\mathbb{T}$}
\newunicodechar{𝟘}{$\mathbb{0}$}
\newunicodechar{𝟙}{$\mathbb{1}$}
\newunicodechar{𝟚}{$\mathbb{2}$}
\newunicodechar{⋆}{${}_*$}
\newunicodechar{○}{$\gcv$}
\newunicodechar{ᵤ}{${}_u$}
\newunicodechar{⊚}{$\fatsemi$}
\newunicodechar{⟷}{$\leftrightarrow$}
\newunicodechar{⟶}{$\longrightarrow$}
\newunicodechar{⟪}{$\ll$}
\newunicodechar{⟫}{$\gg$}
\newunicodechar{⊎}{$\uplus$}
\newunicodechar{ₗ}{$_l$}
\newunicodechar{ᵣ}{$_r$}
\newunicodechar{ₙ}{$_n$}
\newunicodechar{❰}{$\llparenthesis$}
\newunicodechar{❱}{$\rrparenthesis$}

@@

Below, we show code that defines types corresponding to bits (booleans),
two-bits, three-bits, and four-bits. We then define an operator that
builds a controlled version of a given combinator $c$. This controlled
version takes an additional ``control'' bit and only applies $c$ if
the control bit is true. The code then iterates the control operation
several times starting from boolean negation.

@@

By construction, the \AgdaFunction{TOFFOLI} function takes three bits,
and negates the third if the first two are both true. As
Toffoli~\cite{Toffoli:1980} demonstrated, this function is universal
for classical reversible circuits assuming it is possible to allocate
and de-allocate ancilla bits. Indeed without using ancilla bits, it is
not possible to use compositions of \AgdaFunction{TOFFOLI} functions
to implement more general versions that are controlled by more than
two bits (for example, \AgdaFunction{CTOFFOLI}). The proof is simple:
the \AgdaFunction{TOFFOLI} function depends on two control bits and
possibly negates a third; when used in a circuit with four bits, the
unused bit can be either state, which means that
\AgdaFunction{TOFFOLI} generates an even permutation. The function
\AgdaFunction{CTOFFOLI} is however an odd permutation which is
unreachable from even permutations.
This function will however be definable using composition of
\AgdaFunction{TOFFOLI} once we introduce ancilla bits in the next section.

@@

Note that in the construction of \AgdaFunction{TOFFOLIₙ} only wire manipulating operators
(multiplicative operators), ancilla allocation / de-allocation and \AgdaFunction{TOFFOLI}
are used.
\begin{figure}[ht]
  \PIFDtoffoli{}
\caption{\label{fig:toff}Generalized Toffoli Gates}
\end{figure}
